Exponential Integrals\\ [1ex]

### 2022-05-16 draft2.tex
Remove some hats

\begin{definition}
A holomorphic function $\hat{f}$ in an open disk $D\subset \C_{\zeta}$ has a simple singularity at $\omega$, adherent to $D$, if there exist $\alpha\in\C$ and a germs of analytic functions at
the origin $\hat{\Phi}(\zeta)\in\C\lbrace\zeta\rbrace$, such that
\begin{equation}
\hat{f}(\zeta)=\frac{\alpha}{2\pi i(\zeta-\omega)}+\frac{1}{2\pi i}\log(\zeta-\omega)\hat{\phi}(\zeta-\omega)+\text{hol. fct.}
\end{equation}
for all $\zeta\in D$ close enough to $\omega$. The constant $\alpha$ is called the residuum and $\hat{\phi}$ the minor.
\end{definition}

The holomorphic function $\hat{\phi}$ associated with the logarithmic singularity can be obtained by considering the analytic continuation of $\hat{f}$ across the logarithmic branch cut
\begin{equation}
\hat{\phi}(\zeta)=\hat{f}(\zeta+\omega)-\hat{f}(\zeta e^{-2\pi i}+\omega)
\end{equation}
where with $\hat{f}(\zeta e^{-2\pi i}+\omega)$ is the analytic continuation of $\hat{f}$ along the circular
path $\omega+\zeta e^{-2\pi i t}$ with $t\in [0,1]$.

@@

@@

\begin{align*}\label{formula1}
\hat{\varphi}_{\alpha}(\zeta) & = \partial^{\textcolor{red}{3/2}}_{\zeta \text{ from }\zeta_\alpha} \left( \int_{\mathcal{C}_\alpha(\zeta)} \nu \right) \\
& = \textcolor{red}{\left(\tfrac{\partial}{\partial \zeta}\right)^2}\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\zeta_\alpha}^\zeta (\zeta-\zeta')^{-1/2} \textcolor{red}{\left( \int_{\mathcal{C}_\alpha(\zeta')} \nu \right)}\,d\zeta',
\end{align*}

@@

\section{Airy exponential integral}
By definition,
\[ \Ai(x) \defeq \frac{1}{2\pi i}\int_{-\infty e^{-i\frac{\pi}{3}}}^{\infty e^{i\frac{\pi}{3}}} e^{t^3/3 - xt}\,dt. \]
Define $I(z)$ by the change of coordinates $z=x^{3/2}$, $I(z)=-2\pi iz^{-1/3}\Ai(x)$. This new function satisfies the ODE\footnote{$\Ai(x)$ solves the Airy equation $y''=xy$.}
\begin{equation}\label{eq:I}
I''(z)-\frac{4}{9}I(z)+\frac{I'(z)}{z}-\frac{1}{9}\frac{I(z)}{z^2} = 0.
\end{equation}
A formal solution of \eqref{eq:I} can be computed by making the following ansatz 
\begin{equation}
\tilde{I}(z)=\sum_{k\in\N^2}U^ke^{-\lambda\cdot k z}z^{-\tau\cdot k}w_k(z)
\end{equation}
with $U^{(k_1,k_2)}=U_1^{k_1}U_2^{k_2}$ and $U_1,U_2\in\C$ are constant parameter, $\lambda=(\frac{2}{3},-\frac{2}{3})$, $\tau=(\frac{1}{2},\frac{1}{2})$, and $\tilde{w}_k(z)\in\C[[z^{-1}]]$. In addition, we can check that the only non zero $\tilde{w}_k(z)$ occurs at $k=(1,0)$ and $k=(0,1)$, therefore
\begin{equation}
\tilde{I}(z)=U_1e^{-2/3z}z^{-1/2}\tilde{w}_{+}(z)+U_2e^{2/3z}z^{-1/2}\tilde{w}_{-}(z)
\end{equation}  
where from now on we denote $\tilde{w}_+(z)=\tilde{w}_{(1,0)}(z)$ and $\tilde{w}_-(z)=\tilde{w}_{(0,1)}(z)$. In particular, $\tilde{w}_+(z)$ and $\tilde{w}_-(z)$ are formal solution of 
\begin{align}
\label{eq:w+} \tilde{w}_+''-\frac{4}{3}\tilde{w}_+'+\frac{5}{36}\frac{\tilde{w}_+}{z^2}=0\\
\label{eq:w-} \tilde{w}_-''+\frac{4}{3}\tilde{w}_-'+\frac{5}{36}\frac{\tilde{w}_-}{z^2}=0
\end{align}
Taking the Borel transform of \eqref{eq:w+}, \eqref{eq:w-} we get
\begin{align*}
&\zeta^2\hat{w}_{+}(\zeta)+\frac{4}{3}\zeta\hat{w}_{+}+\frac{5}{36}\zeta\ast\hat{w}_{+}=0\\
&\zeta^2\hat{w}_{+}(\zeta)+\frac{4}{3}\zeta\hat{w}_{+}+\frac{5}{36}\int_0^\zeta(\zeta-\zeta')\hat{w}_{+}(\zeta')d\zeta'=0
\end{align*}
\begin{align*}
&\zeta^2\hat{w}_{-}(\zeta)-\frac{4}{3}\zeta\hat{w}_{-}+\frac{5}{36}\zeta\ast\hat{w}_{-}=0\\
&\zeta^2\hat{w}_{-}(\zeta)-\frac{4}{3}\zeta\hat{w}_{-}+\frac{5}{36}\int_0^\zeta(\zeta-\zeta')\hat{w}_{-}(\zeta')d\zeta'=0
\end{align*}
and taking derivatives we get
\begin{align*}
&\zeta(\frac{4}{3}+ \zeta)\hat{w}_{+}''+(\frac{8}{3}+4\zeta)\hat{w}_+'+\frac{77}{36}\hat{w}_{+}=0 & \\
&\frac{4}{3}\zeta( 1+ \frac{3}{4}\zeta)\hat{w}_{+}''+(\frac{8}{3}+4\zeta)\hat{w}_+'+\frac{77}{36}\hat{w}_{+}=0 & \\
&\qquad u(1-u)\hat{w}_+''(u)+(2-4u)\hat{w}_+'(u)-\frac{77}{36}\hat{w}_+(u)=0 & u=-\frac{3}{4}\zeta\\
%&\qquad u(1-u)\hat{w}_-''(u)+(2-4u)\hat{w}_-'(u)-\frac{77}{36}\hat{w}_-(u) & u=\frac{3}{4}\zeta
\end{align*} 
\begin{align*}
&\zeta(-\frac{4}{3}+ \zeta)\hat{w}_{-}''+(-\frac{8}{3}+4\zeta)\hat{w}_-'+\frac{77}{36}\hat{w}_{-}=0 & \\
&\frac{4}{3}\zeta(-1+ \frac{3}{4}\zeta)\hat{w}_{-}''+(-\frac{8}{3}+4\zeta)\hat{w}_-'+\frac{77}{36}\hat{w}_{-}=0 & \\
&\qquad u(1-u)\hat{w}_-''(u)+(2-4u)\hat{w}_-'(u)-\frac{77}{36}\hat{w}(u)=0 & u=\frac{3}{4}\zeta
\end{align*} 
Notice that the latter equations are hypergeometric, hence a solution is given by 
\begin{align}
\label{hat+}\hat{w}_+(\zeta)=\mathit{c}_1 \, {}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,-\frac{3}{4}\zeta\right)\\
\label{hat-}\hat{w}_-(\zeta)=\mathit{c}_2 \, {}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,\frac{3}{4}\zeta\right)
\end{align}
for some constants $\mathit{c}_1, \mathit{c}_2\in\C$ (see DLMF 15.10.2). In addition $\hat{w}_{\pm}(\zeta)$ have a log singularity respectively at $\zeta=\mp\frac{4}{3}$, therefore they are $\lbrace\mp\frac{4}{3}\rbrace $-resurgent functions.\footnote{The solution we find are equal to the ones in DLMF $\mathsection 9.7$. They also agree with slide 10 of Maxim's talk for ERC and with the series (6.121) in Sauzin's book. However they do not agree with (2.16) in Mari\~no's Diablerets.}

%\begin{remark}
%In \cite{Marino-diableret}, Mari\~{n}o studies the example of the Airy function and its resurgent properties. According to his notation
%\begin{equation}
%Ai(x)=\frac{1}{2x^{1/4}\sqrt{\pi}}e^{-\frac{2}{3}x^{3/2}}\varphi_1(x^{-3/2})
%\end{equation}
%\begin{equation}
%Bi(x)=\frac{1}{2x^{1/4}\sqrt{\pi}}e^{\frac{2}{3}x^{3/2}}\varphi_2(x^{-3/2})
%\end{equation}
%with \[\varphi_{1,2}(z)=\sum_{k\geq 0}\frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^k\frac{\Gamma\left(k+\frac{1}{6}\right)\Gamma\left(k+\frac{5}{6}\right)}{k!}z^k.\]
%In particular, the Borel transform of $\varphi_1(z)$ and $\varphi_2(z)$ are respectively 
%\begin{align}
%\label{Marino_hat}
%\hat{\varphi}_1(\zeta)&={}_1F_2\left(\frac{1}{6},\frac{5}{6};1;-\frac{3}{4}\zeta\right)\\
%\label{Marino_hat2}\hat{\varphi}_2(\zeta)&={}_1F_2\left(\frac{1}{6},\frac{5}{6};1;\frac{3}{4}\zeta\right)
%\end{align} 
% In particular, we notice that $\hat{w}_+(\zeta)$ and $\hat{w}_-(\zeta)$ in \eqref{eq:w+}, \eqref{eq:w-} are (up to a constant) the first derivatives of
%\begin{align*}
%\hat{w}_+(\zeta)&\propto\frac{\dd}{\dd\zeta}\hat{\varphi}_1(\zeta)\\
%\hat{w}_-(\zeta)&\propto\frac{\dd}{\dd\zeta}\hat{\varphi}_2(\zeta)
%\end{align*} 
%\end{remark}

Our next goal is to prove that the Borel transform of $\tilde{I}(z)$ can be written in terms of $1/f'(f^{-1}(\zeta))$, namely formula \eqref{formula1}. It is convenient to consider the two asymptotic formal solutions separately, namely we define

\begin{align}
\tilde{I}_{-1}(z)\defeq e^{-2/3z}z^{-1/2}\tilde{w}_+(z)=\colon z^{-1/2}\tilde{u}_+(z) \\
\tilde{I}_{1}(z)\defeq e^{2/3z}z^{-1/2}\tilde{w}_-(z)=\colon z^{-1/2}\tilde{u}_-(z)
\end{align}

In particular, $\tilde{u}_{\pm}(z)$ are solutions of

\begin{equation}\label{eq:u}
\tilde{u}''(z)-\frac{4}{9}\tilde{u}(z)+\frac{5}{36}\frac{\tilde{u}(z)}{z^2}=0
\end{equation}

with asymptotic behaviour $\tilde{u}_\pm(z)\sim O(e^{\pm 2/3 z})$ as $z\to\infty$.

The Borel transforms $\hat{u}_{\pm}(\zeta)$ solve the same equation
\begin{align*}
&\zeta^2\hat{u}-\frac{4}{9}\hat{u}+\frac{5}{36}\zeta\ast\hat{u}\\
&\zeta^2\hat{u}-\frac{4}{9}\hat{u}+\frac{5}{36}\int_0^\zeta(\zeta-\zeta')\hat{u}(\zeta')d\zeta'\\
&\text{taking derivatives is equivalent to} \\
&(\zeta^2-\frac{4}{9})\hat{u}''(\zeta)+4\zeta\hat{u}'(\zeta)+\frac{77}{36}\hat{u}(\zeta)=0
\end{align*}

and Mathematica gives the following solutions
\begin{align*}
\hat{u}(\zeta)&=c_1 \, {}_{1}F_{2}\left(\frac{7}{12},\frac{11}{12},\frac{1}{2},\frac{9}{4}\zeta^2\right) +\frac{3i}{2}\zeta c_2 \, {}_{1}F_{2}\left(\frac{13}{12},\frac{17}{12},\frac{3}{2},\frac{9}{4}\zeta^2\right)= &\\
&=c_1\frac{\Gamma(\frac{13}{12})\Gamma(\frac{17}{12})}{2\sqrt{\pi}}\left({}_{1}F_{2}\left(\frac{7}{12},\frac{11}{12},\frac{1}{2},\frac{1}{2}-\frac{3}{4}\zeta\right)- {}_{1}F_{2}\left(\frac{7}{12},\frac{11}{12},\frac{1}{2},\frac{1}{2}+\frac{3}{4}\zeta\right)\right) & \text{see DLMF 15.8.27} \\
&\qquad +\frac{3i}{2}\zeta c_2 \left(\frac{\Gamma(\frac{7}{12})\Gamma(\frac{11}{12})}{3\zeta\Gamma(-\frac{1}{2})\Gamma(2)}\right)\left( {}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},{2},\frac{1}{2}-\frac{3}{4}\zeta\right)-{}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},{2},\frac{1}{2}+\frac{3}{4}\zeta\right)\right)  & \text{see DLMF 15.8.28}\\
&=\left(c_1\frac{\Gamma(\frac{13}{12})\Gamma(\frac{17}{12})}{2\sqrt{\pi}} -c_2i\frac{\Gamma(\frac{7}{12})\Gamma(\frac{11}{12})}{4\sqrt{\pi}}\right)\, {}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,\frac{1}{2}-\frac{3}{4}\zeta\right)  + & \\
&\qquad\qquad +\left(c_1\frac{\Gamma(\frac{13}{12})\Gamma(\frac{17}{12})}{2\sqrt{\pi}} +c_2i\frac{\Gamma(\frac{7}{12})\Gamma(\frac{11}{12})}{4\sqrt{\pi}}\right)\, {}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,\frac{1}{2}+\frac{3}{4}\zeta\right) &  
\end{align*}
Since $\hat{u}_+$ has a simple singularity at $\zeta=-2/3$ and $\hat{u}_-$ has a simple singularity at $\zeta=2/3$, we have
\begin{align*}
\hat{u}_+(\zeta)&=C_1 T_{-\tfrac{2}{3}}\;{}_{2}F_{1}\left(\frac{7}{6},\frac{11}{6},2,-\frac{3}{4}\zeta\right)=C_1 T_{-\tfrac{2}{3}}\;\hat{w}_+(\zeta)\\
\hat{u}_-(\zeta)&= C_2 T_{\tfrac{2}{3}}\;{}_{2}F_{1}\left(\frac{7}{6},\frac{11}{6},2,\frac{3}{4}\zeta\right)= C_2 T_{\tfrac{2}{3}}\;\hat{w}_-(\zeta)
\end{align*}

\begin{lemma}
The following identity holds true
\begin{equation}
{}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\frac{9}{4}\zeta^2\right)=\frac{1}{1-u^2}\qquad \zeta=\frac{u^3}{3}-u
\end{equation}
\end{lemma}
\begin{proof}From the special case of hypergeometric function (see 15.4.14 DLMF) we have the following identity:
\begin{align*}
{}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\frac{9}{4}\zeta^2\right) &= \frac{\cos(y)}{\cos(3y)} & 3y=\arcsin\left(\frac{3}{2}\zeta\right)\\
&=\frac{\cos(y)}{\cos(2y)\cos(y)-\sin(2y)\sin(y)} & \\
&=\frac{1}{\cos(2y)-2\sin^2(y)} & \\
&=\frac{1}{1-4\sin^2(y)} & \zeta=2\sin(y)-\frac{8}{3}\sin^3(y)
\end{align*}
Therefore, if $u\defeq -2\sin(y)$, we have $\zeta=\frac{u^3}{3}-u=f(u)$ and \[{}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\frac{9}{4}\zeta^2\right)=\frac{1}{1-u^2}=-\frac{1}{f'(u)}\]
\end{proof}

Then equations \eqref{formula1} is equivalent to: \textbf{[Now that we've switched to the Riemann-Liouville derivative, the claim that was referenced here no longer involves $\nu/df$. The calculation above is still useful, but it should go somewhere else.]}

>>>>

\begin{definition}
A function $f$ defined in an open disk $D\subset \C_{\zeta}$ has a simple singularity at $\omega$, adherent to $D$, if there exist $\alpha\in\C$ and a germ of analytic functions at
the origin $\hat{\phi}(\zeta)\in\C\lbrace\zeta\rbrace$, such that
\begin{equation}
f(\zeta)=\frac{\alpha}{2\pi i(\zeta-\omega)}+\frac{1}{2\pi i}\text{Log}(\zeta-\omega)\hat{\phi}(\zeta-\omega)+\text{hol. fct.}
\end{equation}
for all $\zeta\in D$ close enough to $\omega$. The constant $\alpha$ is called the residuum and $\hat{\phi}$ the minor. $\mathrm{Log}(\zeta)$ is the principal branch of $\log(\zeta)$ in $D$; different branches of $\log(\zeta)$ differs by a multiple of $\hat{\phi}(\zeta)$, hence they define the same singularity $\overset{\triangledown}{\phi} $. 
\end{definition}

The holomorphic function $\hat{\phi}$ associated with the logarithmic singularity can be obtained by considering the analytic continuation of $\hat{f}$ across the logarithmic branch cut
\begin{equation}
\hat{\phi}(\zeta)={f}(\zeta+\omega)-{f}(\zeta e^{-2\pi i}+\omega)
\end{equation}
where with $\hat{f}(\zeta e^{-2\pi i}+\omega)$ is the analytic continuation of $\hat{f}$ along the circular
path $\omega+\zeta e^{-2\pi i t}$ with $t\in [0,1]$.

@@

\begin{equation}\label{exp-int}

@@

\begin{multline}\label{formula1}
\hat{\varphi}_{\alpha}(\zeta)=\partial^{\textcolor{red}{3/2}}_{\zeta \text{ from }\zeta_\alpha} \left( \int_{\mathcal{C}_\alpha(\zeta)}\nu \right)=\textcolor{red}{\left(\tfrac{\partial}{\partial \zeta}\right)^2}\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\zeta_\alpha}^\zeta (\zeta-\zeta')^{-1/2} \textcolor{red}{\left( \int_{\mathcal{C}_\alpha(\zeta')} \nu \right)}\,d\zeta',
\end{multline}

@@

\section{Airy exponential integral: Stokes constants using fractional derivative formula and Borel transform computation}

We study the resurgent properties of the Airy function $\mathrm{Ai}(x)$. As in section 3.2 {\tt airy-resurgence}, it is convenient to change coordinates and turn $\mathrm{Ai}(x)$ in exponential integral like \eqref{exp-int}: with the substitution $t=-2ux^{1/2}$, we can rewrite the Airy integral as
\[ \Ai(x) = x^{1/2}\;\frac{i}{\pi} \int_{x^{-1/2} \mathcal{C}_+} \exp\left[-\tfrac{2}{3}x^{3/2} \left(4u^3 - 3u\right)\right]\,du, \]
where $\mathcal{C}_+$ is the path $\theta \mapsto \cosh(\theta - \tfrac{2}{3}\pi i)$. When $x \in [0, \infty)$, this leads to the expression

\[ I_+(z) \defeq \int_{\mathcal{C}_+} \exp\left[-\tfrac{2}{3} z \left(4u^3 - 3u\right)\right]\,du. \]
In our general picture of exponential integrals, $f = \tfrac{2}{3}(4u^3 - 3u)$ and $\nu = du$.

Since $\mathrm{Ai}(x)$ is a solution of Airy equation, $I(z)$ is a solution of 
\begin{equation}\label{eq:I}
I''(z)-\frac{4}{9}I(z)+\frac{I'(z)}{z}-\frac{1}{9}\frac{I(z)}{z^2} = 0.
\end{equation}

From the general theory of linear ODE, \eqref{eq:I} has a two--parameter formal integral solution $\tilde{I}(z)\in z^{-1/2}\C[\![z^{-1}]\!]$

\begin{equation}
\tilde{I}(z)=U_1e^{-2/3z}z^{-1/2}\tilde{W}_{+}(z)+U_2e^{2/3z}z^{-1/2}\tilde{W}_{-}(z)
\end{equation}
where $\tilde{W}_+(z)=1+\sum_{n=1}^{\infty}a_{+,n}z^{-n}$ and $\tilde{W}_-(z)=1+\sum_{n=1}^{\infty}a_{-,n}z^{-n}$ are the unique formal solutions of 
\begin{align}
\label{eq:w+} \tilde{W}_+''-\frac{4}{3}\tilde{W}_+'+\frac{5}{36}\frac{\tilde{W}_+}{z^2}=0\\
\label{eq:w-} \tilde{W}_-''+\frac{4}{3}\tilde{W}_-'+\frac{5}{36}\frac{\tilde{W}_-}{z^2}=0
\end{align}

Notice that $I_+(z)$ is asymptotic to $U_1e^{-2/3z}z^{-1/2}\tilde{W}_{+}(z)$ as $\Re z\to+\infty$. Recursively, we determine $a_{\pm,n}$: set $a_{\pm,0}=1$, then

\begin{align*}
a_{\pm, n+1}=\mp\frac{3}{4}\left(n+\frac{1}{6}\right)\left(n+\frac{5}{6}\right)\frac{1}{n+1}a_{\pm,n} \, \qquad n\geq 0
\end{align*}
hence $a_{\pm,n}=\frac{1}{2\pi}(\mp 1)^n\left(\frac{3}{4}\right)^{n}\Gamma(n+\tfrac{1}{6})\Gamma(n+\tfrac{5}{6})\frac{1}{n!}$ for $n\geq 1$ and they are factorially divergent. Thus, $\tilde{W}_{\pm}(z)$ are Gevrey-1 series.

We now compute the  Borel transform $\tilde{w}_{\pm}(\zeta)=\mathcal{B}\tilde{W}_{\pm}$: it can be done in different ways, on one hand we can compute the Borel transform of $\tilde{W}_{\pm}$ via their explicit formal expansion, namely

\begin{align*}
\tilde{w}_{\pm}(\zeta)&=\delta+\sum_{n\geq 1}a_{\pm,n}\frac{\zeta^{n-1}}{(n-1)!}=\delta+\sum_{n=0}^{\infty}\frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n+1}\frac{\Gamma\left(n+\frac{7}{6}\right)\Gamma\left(n+\frac{11}{6}\right)}{(n+1)!}\frac{\zeta^n}{n!}\\
&=\delta\mp\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right)
\end{align*}
On the other hand, we can look at the Borel transform of the ODEs \eqref{eq:w+}\eqref{eq:w-} and solve them. Thanks to properties of $\mathcal{B}$, $\tilde{w}_{\pm}(\zeta)$ are solution of

\begin{align*}
&\zeta^2\tilde{w}_{\pm}(\zeta)\pm\frac{4}{3}\zeta\tilde{w}_{\pm}+\frac{5}{36}\zeta\ast\tilde{w}_{\pm}=0\\
&\zeta^2\tilde{w}_{\pm}(\zeta)\pm\frac{4}{3}\zeta\tilde{w}_{\pm}+\frac{5}{36}\int_0^\zeta(\zeta-\zeta')\tilde{w}_{\pm}(\zeta')d\zeta'=0
\end{align*}

\color{Plum}
Differentiating twice, we get the following equations

\begin{equation}\label{eq:hypergeomtric w}
\zeta\left(\pm\frac{4}{3}+ \zeta\right)\tilde{w}_{+}''+\left(\pm\frac{8}{3}+4\zeta\right)\tilde{w}_+'+\frac{77}{36}\tilde{w}_{+}=0 
\end{equation}

which after the change of coordinates $u=\mp\frac{3}{4}\zeta$ they are hypergeometric equations with parameters $\left(\frac{7}{6}, \frac{11}{6}; 2\right)$. However, being a solution of \eqref{eq:hypergeomtric w} is not equivalent to being a solution of the integral equation; it holds only up to constants. In our example, the constant is given by $\delta$, hence we conclude

\begin{align}
\label{hat+}\hat{w}_+(\zeta)=\delta+\mathit{c}_1 \, {}_{2}F_{1}\left(\frac{7}{6},\frac{11}{6},2,-\frac{3}{4}\zeta\right)\\
\label{hat-}\hat{w}_-(\zeta)=\delta+\mathit{c}_2 \, {}_{2}F_{1}\left(\frac{7}{6},\frac{11}{6},2,\frac{3}{4}\zeta\right)
\end{align}
for some constants $\mathit{c}_1, \mathit{c}_2\in\C$.

\color{black}
In Theorem \eqref{thm:maxim} we prove that the Borel transform of $\tilde{\varphi}_{\alpha}$ can be computed by the fractional derivative formula ~\eqref{int:deriv-formula}. This method allows to uniquely determined the constants $U_1,U_2$ that appear in the formal integral solution $\tilde{I}(z)$. Indeed, $\tilde{I}$ is a solution of an homogeneous linear ODE and $\tilde{I}_+(z)=U_1e^{-2/3z}z^{-1/2}\tilde{W}_+(z)$ for a particular choice of $U_1$. %In order to compute the Stokes constants we will first use the fractional derivative formula to compute the correct normalization of \[\hat{w}_\pm(\zeta)=\delta\mp \frac{5}{48}{}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right).\]   
\begin{lemma}\label{claim 2}
The following formula holds true
\[ \partial^{3/2}_{\zeta \text{ from } 2/3} \left( \int_{\mathcal{C}_+(\zeta)} \nu \right) = -i \frac{\sqrt{\pi}}{2}\,\hat{w}_+(\zeta-2/3), \]
for any $\zeta\in [2/3,+\infty)$.
\end{lemma}
\begin{proof}
In our general picture of exponential integrals, for $I_+(z)$ the thimble $\mathcal{C}_+$ is parametrized as the path $\theta \mapsto \cosh(\theta - \tfrac{2}{3}\pi i)$, $f = \tfrac{2}{3}(4u^3 - 3u)$ and $\nu = du$. Hence,
\begin{align*}
\int_{\mathcal{C}_+(\zeta)} \nu & = \int_{\mathcal{C}_+(\zeta)} du \\
& = u \Big|_{\operatorname{start} \mathcal{C}_+(\zeta)}^{\operatorname{end} \mathcal{C}_+(\zeta)}.
\end{align*}
Since $4u^3 - 3u$ is the third Chebyshev polynomial, and $\cosh$ is $2\pi$-periodic in the imaginary direction, the start and end points of $\mathcal{C}_+(\zeta)$ are characterized by
\begin{align*}
u & = \cosh(\mp\theta - \tfrac{2}{3}\pi i) \\
\zeta & = \tfrac{2}{3} \cosh(3\theta),
\end{align*}
so
\begin{align*}
\int_{\mathcal{C}_+(\zeta)} \nu & = \cosh(\theta - \tfrac{2}{3}\pi i) - \cosh(-\theta - \tfrac{2}{3}\pi i) \\
& = \big[\cosh(\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
& \quad - \big[\cosh(-\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(-\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
& = 2\sinh(\theta) \sinh(-\tfrac{2}{3}\pi i) \\
& = -i\sqrt{3}\,\sinh(\theta)
\end{align*}
with $\tfrac{3}{2} \zeta = \cosh(3\theta)$. Let $\xi = \tfrac{1}{2}(1 - \tfrac{3}{2}\zeta)$, and notice that $\xi = -\sinh(\tfrac{3}{2} \theta)^2$ at the start and end points. The identity \textbf{[DLMF~15.4.16]}
\[ \sinh(\theta) = \tfrac{2}{3} \sinh(\tfrac{3}{2} \theta)\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; -\sinh(\tfrac{3}{2} \theta)^2\big) \]
then shows us that
\[ \frac{i}{\sqrt{3}} \int_{\mathcal{C}_+(\zeta)} \nu = \tfrac{2}{3} (-\xi)^{1/2}\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big). \]

Now we can evaluate the half-integral of $\int_{\mathcal{C}_+} \nu$ using Bateman's fractional integral formula for hypergeometric functions~\textbf{[Koornwinder, \S 4.1]}.
\begin{align*}
\partial^{-1/2}_{\zeta \text{ from } 2/3} \left( \int_{\mathcal{C}_+(\zeta)} \nu \right) & = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{2/3}^\zeta (\zeta - \zeta')^{-1/2} \left( \int_{\mathcal{C}_+(\zeta')} \nu \right)\,d\zeta' \\
& = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_0^\xi \tfrac{\sqrt{3}}{2} (\xi' - \xi)^{-1/2} \Big[ -{i}{\sqrt{3}}\,\tfrac{2}{3} (-\xi)^{1/2}\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big) \Big] \,\big( -\tfrac{4}{3}\,d\xi' \big) \\
& = -i \frac{4}{3} \frac{\Gamma\big(\tfrac{3}{2}\big)}{\Gamma(2)} (-\xi)\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \\
& = i \frac{2}{3} \sqrt{\pi}\,\xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big).
\end{align*}
Finally, we differentiate twice using \textbf{[DLMF 15.5.4]} and \textbf{[DLMF 15.5.1]}.
\begin{align*}
\partial^{3/2}_{\zeta \text{ from } 2/3} \left( \int_{\mathcal{C}_+(\zeta)} \nu \right) & = \left(-\tfrac{3}{4} \tfrac{\partial}{\partial \xi}\right)^2 \left[ i \frac{2}{3} \sqrt{\pi}\,\xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
& = i \tfrac{3\sqrt{\pi}}{8} \left(\tfrac{\partial}{\partial \xi}\right)^2 \left[ \xi\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
& = i \tfrac{3\sqrt{\pi}}{8}\,\tfrac{\partial}{\partial \xi} \left[ {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 1; \xi\big) \right] \\
& = i \tfrac{\sqrt{\pi}}{8}\,\tfrac{5}{12}\, {}_2F_1\big(\tfrac{7}{6}, \tfrac{11}{6}; 2; \xi\big).
\end{align*}
\end{proof}
Analogously, we can compute the correct constants for $\hat{w}_-(\zeta)$:

\begin{lemma}\label{claim 3}
For any $\zeta\in (-\infty,-2/3]$
\[ \partial^{3/2}_{\zeta \text{ from } -2/3} \left( \int_{\mathcal{C}_-(\zeta)} \nu \right) = - \frac{\sqrt{\pi}}{2}\,\hat{w}_-(\zeta+2/3). \]
\end{lemma}
\begin{proof}
Let $\mathcal{C}_-$ is the path $\theta \mapsto -\cosh(\theta - \tfrac{2}{3}\pi i)$, when $x \in [0, \infty)$ 
\[ I_-(z) = \int_{\mathcal{C}_-} \exp\left[-\tfrac{2}{3} z \left(4u^3 - 3u\right)\right]\,du. \]
In our general picture of exponential integrals, $f = \tfrac{2}{3}(4u^3 - 3u)$ and $\nu = du$. Hence,
\begin{align*}
\int_{\mathcal{C}_-(\zeta)} \nu & = \int_{\mathcal{C}_-(\zeta)} du \\
& = u \Big|_{\operatorname{start} \mathcal{C}_-(\zeta)}^{\operatorname{end} \mathcal{C}_-(\zeta)}.
\end{align*}
The start and end points of $\mathcal{C}_-(\zeta)$ are characterized by
\begin{align*}
u & = -\cosh(\mp\theta - \tfrac{2}{3}\pi i) \\
\zeta & = -\tfrac{2}{3} \cosh(3\theta),
\end{align*}
so
\begin{align*}
\int_{\mathcal{C}_-(\zeta)} \nu & =- \cosh(\theta - \tfrac{2}{3}\pi i) + \cosh(-\theta - \tfrac{2}{3}\pi i) \\
& =- \big[\cosh(\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
& \quad + \big[\cosh(-\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(-\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
& = 2\sinh(\theta) \sinh(\tfrac{2}{3}\pi i) \\
& = i\sqrt{3}\,\sinh(\theta)
\end{align*}
with $\tfrac{3}{2} \zeta = -\cosh(3\theta)$. Let $\xi = \tfrac{1}{2}(1 + \tfrac{3}{2}\zeta)$, and notice that $\xi =- \sinh(\tfrac{3}{2} \theta)^2$ at the start and end points. The identity \textbf{[DLMF~15.4.16]}
\[ \sinh(\theta) = \tfrac{2}{3} \sinh(\tfrac{3}{2} \theta)\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; -\sinh(\tfrac{3}{2} \theta)^2\big) \]
then shows us that
\[ -\frac{i}{\sqrt{3}} \int_{\mathcal{C}_-(\zeta)} \nu = \tfrac{2}{3} (-\xi)^{1/2}\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big). \]
